%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Modified Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.0 (01/03/2021)
% 
% Author
% Joyce Shendre(https://joyceshendre07)
% Repository
% https://github.com/JoyceShendre/Modified-Deedy-Resume
% Original author of Deedy Resume:
% Debarghya Das (http://debarghyadas.com)
% His repository:
% https://github.com/deedydas/Deedy-Resume
%
%

%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
\usepackage[utf8]{inputenc}
\usepackage{eurosym}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Joyce}{Shendre}{ 
\href{mailto:me@joyceshendre07@gmail.com}{\bf hi@joyceshendre07@gmail.com} | \bf +919172443091 | \urlstyle{same}\href{https://github.com/JoyceShendre}{\bf Github} |
\urlstyle{same}\href{https://www.hackerrank.com/joyce_shendre}{\bf Hackerrank} |
\urlstyle{same}\href{https://www.linkedin.com/in/joyce-
shendre/}{\bf Linkedin}} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.66\textwidth} 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\subsection{St. Vincent Pallotti college of engineering}
\descript{Bachelor of Engineering (Hons.) Computer Engineering}
\location{08 August \textbf{2016} -26 November \textbf{2020} | Nagpur,Maharashtra, IN}
\textbf{Classification: First Class,CGPA: 8.19/10} 
\sectionsep 
\subsection{Dr Babasaheb Ambedkar College of Science}
\location{Brahmapuri,Chandrapur,Maharashtra,IN}
\textbf{}{HSC- June 2014 | Percentage- 64}
\sectionsep 
\subsection{Nevjabai Hitkarni Girl's High School}
\textbf{}{SSC- June 2012 | Percentage- 84 }
\subsection{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Konverge AI Pvt. Ltd.}
\descript{| Software Engineer }
\location{Nov \textbf{2020 } – Present | Nagpur,MH, IN}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Developed back-end of full-stack applications by applying experience in
Node-Js, PostgreSql, MongoDB and JavaScript programming language.
\item Lead development of the user back-end website in Node-Js.
\end{tightemize}
\sectionsep

\runsubsection{Sacchidanand U-Tech}
\descript{| Software Developer Intern}
\location{June \textbf{2020 } – Oct | Nagpur,MH,IN}
\begin{tightemize}
\item Developed REST APIs for Home-Automation System.
\item Partnered with development team on product development,
application support plans, and prototype programs. Built project plan,
designed database for the system.
\end{tightemize}
\sectionsep

\runsubsection{ANV Infotech Pvt. Ltd}
\descript{| Software Developer Intern}
\location{May \textbf{2019 } - June \textbf{2019 } | Nagpur,MH,IN | Website: HighLand Glory}
\begin{tightemize}
\item 
Built a website for a celebration hall
named High-Land Glory. The celebration hall required to add booking system
via calendar displayed on the home page of the website.
\end{tightemize}
\sectionsep

\runsubsection{Infoverse Tech Services}
\descript{| Software Developer Intern}
\location{Dec \textbf{2018 } - Mar \textbf{2019 } | Nagpur,MH,IN | Website: Best in Offers- http://bestinoffers.com/}
\begin{tightemize}
\item 
Built an e- commerce website which fetches
the best offers from various shopping sites and shows them on a single page.
\end{tightemize}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Chat-Bot}
\descript{| NodeJS, APIs, Heroku}
\location{May \textbf{2020 }}
\begin{tightemize}
\item A chatbot for one to one chatting experience,creating a room, sending user location etc. using web socket packages in NodeJs applications.
\item The whole end to end solution is deployed on the Heroku and can be accessed on any social messaging service.
\bf
\href{https://chat-app-j07.herokuapp.com/}{ChatApp}{}
\end{tightemize}
\sectionsep

\runsubsection{Anti-Theft Wheel Lock Tracking System}
\descript{IoT}
\location{ Oct \textbf{2020 }}
\begin{tightemize}
\item This System can be the most efficient tools that can be used to control vehicle encroachment on parking places. With the aim to design and develop GPS based anti-theft wheel lock activity tracker.

\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\end{minipage}%
\hfill
\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{\textbf{Over 5000 lines:}}
Python 3\textbullet{} JavaScript \textbullet{} C/C++ \textbullet{} \\ 
\location{\textbf{Over 1000 lines:}}
MySQL \textbullet{} Kibana \textbullet{}\\
PostgreSQL \textbullet{}  \\
\location{\textbf{Familiar:}}
Flutter \textbullet{} Microsoft Graph APIs \textbullet{}
ReactJS \textbullet{ }ELK Stack\textbullet{} Shell
\subsection{VCS \& Build Tools }
Git \textbullet{} Docker \textbullet{} Github Actions
\subsection{Cloud Services}
\location{\textbf{Familiar:}}
AWS \textbullet{} Heroku
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Activities \& Achievements} 

>Member of Computer Society Of India. \\

>Elected to Co-ordinator for technical fest event
under CSI in 2018. \\
>Patent Application On Anti-Theft Wheel Lock Tracking System based on IoT. \\
>Former team member of the R.T.M.Nagpur University Hockey team.
>National Level Hockey Player, former captain of Maharashtra team. \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Certifications}
>Machine Learning A-ZTM: Hands-On Python In Data.
Oct. 2018 \\

>Machine Learning And Data science,Pro Python- TheTechIntern,Nagpur,June 2019 \\

>Introduction to Machine Learning- NPTEL.
Oct.2018 \\

>Data Science- Cognitiveclass.ai (IBM). \\

>Data Science Professional Certificate-IBM(In Progress) \\
>Python for Data Science-Cognitiveclass.ai (IBM). \\
>C - Programming- Unisoft Technologies.\\
>Machine Learning(Stanford University)-Coursera.(In Progress) \\
>Understanding and Visualizing Data with Python-Coursera(In Progress\\
>Understanding and Visualizing Data with Python-Coursera(In Progress)\\

\end{minipage}%
\end{document}  
\documentclass[]{article}
